---
title: 'ILDP2: pilot'
output:
  html_document: default
  pdf_document: default
---

## Prepare the workspace for analysis:
```{r, echo = F}

rm(list=ls())
library(rstan)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

range01 <- function(x){(x-min(x))/(max(x)-min(x))} # function that scales at {0;1}:
```


## Load and assess the data
 (trial - trial number; block - block number; stim - face type [1 or 2]; shock - "shock administered ?"; gsr - galvanic skin response; subject - subject number)
```{r, echo = T}
load('/Users/alebedev/GitHub/ILDP2_pilot/data/rdata.rda')
head(rdata)
```

## Single subject (UNINSTRUCTED version):
```{r, echo = F}
dataList <- list(
  N             = 1,
  T             = 80,
  response      = as.numeric(range01(rdata$gsr)),
  stimulus      = as.integer(rdata$stim),
  shock         = as.integer(rdata$shock)
)

mysamples <- stan(file='/Users/alebedev/GitHub/ILDP2_pilot/stan_models/RW_uninstr_singleSubj.stan',   
                  data=dataList, 
                  #                pars=parameters,
                  iter=2000, 
                  chains=4, 
                  thin=1
)
```


## Plot the results:
```{r}
print(mysamples)
plot(mysamples)

```

## Getting the samples
```{r}
pairs(mysamples)
traceplot(mysamples)

```







# MULTIPLE SUBJECTS (UNFINISHED)

## Emulate some artificial data based on subject 1
```{r, echo = F}
rdata$gsr <- range01(rdata$gsr)
rdata$revtrial <- 0
rdata$revtrial[tail(which(rdata$block==1),1)+1] <- 1
rdata$revtrial[tail(which(rdata$block==2),1)+1] <- 1
rdata$revtrial[tail(which(rdata$block==3),1)+1] <- 1


tail(which(rdata$block==1),1)
rdata <- rbind(rdata,rdata,rdata,rdata,rdata,rdata,rdata,rdata,rdata,rdata)
rdata$subject <- c(rep(1,max(rdata$trial)),
                   rep(2,max(rdata$trial)),
                   rep(3,max(rdata$trial)),
                   rep(4,max(rdata$trial)),
                   rep(5,max(rdata$trial)),
                   rep(6,max(rdata$trial)),
                   rep(7,max(rdata$trial)),
                   rep(8,max(rdata$trial)),
                   rep(9,max(rdata$trial)),
                   rep(10,max(rdata$trial)))
rdata$gsr <- rdata$gsr+sqrt(rnorm(800,0,0.5)^2)
```


## Reorganize the data:
```{r, echo = F}
subjList <- unique(rdata[,'subject'])  # list of subjects x blocks
numSubjs <- length(subjList)  # number of subjects
maxTrials <- max(rdata$trial)


Tsubj <- as.vector(rep(0, numSubjs))
response <- array(0, c(numSubjs, maxTrials) )
stimulus <- array(0, c(numSubjs, maxTrials) )
shock <- array(0, c(numSubjs, maxTrials) )
revtrial <- array(0, c(numSubjs, maxTrials) )


for (i in 1:numSubjs) {
  curSubj      <- subjList[i]
  Tsubj[i] <- sum(rdata$subject == curSubj)  # Tsubj[N]
  useTrials    <- Tsubj[i]
  tmp          <- subset(rdata, rdata$subject == curSubj)
  response[i, 1:useTrials]   <- tmp$gsr
  stimulus[i, 1:useTrials]   <- tmp$stim
  shock[i, 1:useTrials]   <- tmp$shock
  revtrial[i, 1:useTrials]   <- tmp$revtrial
}


dataList <- list(
  N             = numSubjs,
  T             = maxTrials,
  response      = response,
  stimulus      = stimulus,
  shock         = shock,
  Tsubj         = Tsubj
)
```

## Run the model
```{r, echo = F}

### Run Model:
mysamples <- stan(file='/Users/alebedev/GitHub/ILDP2_pilot/stan_models/RW_uninstr_multipleSubj.stan',   
                  data=dataList, 
                  #                pars=parameters,
                  iter=2000, 
                  chains=4, 
                  thin=1
)
```

## Single subject (INSTRUCTED version):
```{r, echo = F}
load('/Users/alebedev/GitHub/ILDP2_pilot/data/rdata.rda')

rdata$revtrial <- 0
rdata[which(rdata$block==2)[1],'revtrial'] <- 1
rdata[which(rdata$block==3)[1],'revtrial'] <- 1
rdata[which(rdata$block==4)[1],'revtrial'] <- 1




dataList <- list(
  N             = 1,
  T             = 80,
  response      = as.numeric(range01(rdata$gsr)),
  stimulus      = as.integer(rdata$stim),
  shock         = as.integer(rdata$shock),
  revtrial      = as.integer(rdata$revtrial)
)

mysamples <- stan(file='/Users/alebedev/GitHub/ILDP2_pilot/stan_models/RW_instr_singleSubj.stan',   
                  data=dataList, 
                  #                pars=parameters,
                  iter=2000, 
                  chains=4, 
                  thin=1
)
```



